The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-22 paper2_JNLS/paper.tex
NM

In particular, we make the following choices
\begin{align}
&\ampscale = \pi^{1/2} \, \etastd \\
&L = \lamfac \lam / \pi \\
&T = \lamfac / \freqp
\end{align}
where $\lamfac$ is an integer to be chosen later. In the physical domain, we will consider an integer multiple of the characteristic wavelength $\xi \in [-\lamfac \lam, \lamfac \lam]$, so that the state variable $u$ is periodic over the  dimensionless domain $\tilde{x} \in [-\pi, \pi]$. We have scaled time accordingly. Finally, our choice of the scale for wave amplitude $\ampscale$ is made to normalize the energy of $u$ to unity. The Hamiltonian framework that we will use relies heavily on the energy, and hence it is more convenient to have the energy normalized to unity rather than making the more common choice of $\etastd$ by itself as the scale for wave amplitude.

>>>>

In particular, we make the following choices
\begin{align}
&\ampscale = \pi^{1/2} \, \etastd \\
&L = \lamfac \lam / \pi \\
&T = \lamfac / \freqp
\end{align}
where $\lamfac$ is an integer to be chosen later. In the physical domain, we will consider an integer multiple of the characteristic wavelength $\xi \in [-\lamfac \lam, \lamfac \lam]$, so that the state variable $u$ is periodic over the  dimensionless domain $\tilde{x} \in [-\pi, \pi]$. We have scaled time accordingly. Finally, our choice of the scale for wave amplitude $\ampscale$ is made to normalize the energy of $u$ to unity. The Hamiltonian framework that we will use relies heavily on the energy, and hence it is more convenient to have the energy normalized to unity rather than making the more common choice of $\etastd$ by itself as the scale for wave amplitude.
\\(Note: The powers in our PNAS paper can be gotten by setting $T = \delta^{-1} \lamfac / \freqp$, since $\delta \sim \sqrt{\depth}$. This is a longer timescale, consistent with the KdV regime of validity. Also, it is a different timescale on either side of the ADC since $\depth$ changes across the ADC.)
